Static Race Detection in OS Kernels by Mining Locking Rules

### 2023-07-23 1.introduction.tex
update

To detect data races effectively, some approaches~\cite{Boyapati:OOPSLA02, 
Anderson:PLDI08, Anderson:PLDI09, Zhou:MICRO19, Flanagan:PASTE01, 
Flanagan:PLDI00, Sadowski:PLATEAU14, ClangThreadSafety, Blackshear:OOPSLA18} 
rely on developers to 
supply annotations that describe the locking discipline such as which lock 
protects a specific data structure field, and detect data races by exploiting 
data structure field accesses that violate these disciplines. For example, 
Clang thread safety analysis~\cite{ClangThreadSafety} requires developers to 
label a variable and the lock to protect it with a {\tt GUARDED\_BY} attribute. 
And then detects data races by finding variable accesses that violate the given 
attribute. However, such annotation-based approaches are not suitable for race 
detection in OS kernels, because even an expert developer can not provide 
accurate annotations, due to poor documentation and complicated logic of OS 
codes.

@@

Dynamic analysis can acquire run-time information such as memory address, and 
thus complex alias analysis can be avoided. Therefore, some 
approaches~\cite{Lochmann:EuroSys19, Lu:SOSP07, Lu:FSE18, Joshi:ASE08, 
Liu:NSDI07} detect data races dynamically to improve precision. They mine 
implicit code rules in softwares by statistically analyzing execution traces, 
and then use the mined rules to detect related bugs. For example, 
LockDoc~\cite{Lochmann:EuroSys19} records accesses to data structure fields and 
lock acquisitions of an instrumented Linux kernel, and then infers locking 
rules from the recorded accesses. After that, LockDoc automatically locates 
data structure fields access that violate the inferred locking rules to detect 
concurrency bugs such as data races. However, dynamic analysis suffers from low 
code coverage, and thus the locking rules inferred through execution traces can 
be imprecise. Besides, dynamic analyses are hard to deploy, because they need 
to run OS kernels with instruments. At last, it is difficult for dynamic 
tools to estimate the harmfulness of a data race, because race conditions are 
hard to trigger by running the checked software~\cite{Fonseca:DSN10, 
Burckhardt:ASPLOS10, Liu:FSE14, Zhou:EASE15}.

@@

(T1) \sys uses an {\em alias-aware rule mining method} to automatically 
deduce locking rules. We observe that an access to a data structure field is 
often protected by the lock in the same data structure as the accessed field. 
And this relationship between accessed field and the protecting lock can be 
effectively inferred from a special data structure named alias 
graph~\cite{Li:ASPLOS22, Kastrinis:CC18}. Specifically, fields in the same data 
structure have the same ancestor in the alias graph, and thus whether an 
accessed field and a specific lock are in the same data structure can be 
inferred by finding a common ancestor in the alias graph. Moreover, with 
benefits from precise field-sensitive alias relationships of alias graph, 
\sys can effectively extract the accessed field and its corresponding 
protecting lock. After obtaining the accessed field and protecting lock pairs, 
\sys calculates the proportion of field accesses protected by a specific 
lock in all field accesses. If the proportion is larger than a given threshold, 
the accessed field is determined to be protected by the protecting lock.

(T2) \sys uses a {\em lock-usage analysis} to filter out false positives 
validating concurrency of code paths. After mining locking rules, \sys detects 
data races by checking whether a given data structure field access violates the 
locking rules. To reduce false negatives, \sys conservatively assumes 
every two functions can be executed concurrently, and thus can introduce false 
positives. However, we observe that each kernel module has an initialization 
phase, after which many functions can be called concurrently by other modules. 
When performing initialization, the kernel module serially initialized the lock 
and prepare other data for subsequent operations. And thus functions with the 
lock initialization and functions called by them tend not to be executed 
concurrently. Based on this observation, \sys extracts all functions 
reachable from the function with a lock initialization operation such as {\tt 
spin\_lock\_init()}, and suppose that this function can not be executed in 
parallel.

>>>>

To detect data races effectively, some approaches~\cite{Boyapati:OOPSLA02, 
Anderson:PLDI08, Anderson:PLDI09, Zhou:MICRO19, Flanagan:PASTE01, 
Flanagan:PLDI00, Sadowski:PLATEAU14, ClangThreadSafety, Blackshear:OOPSLA18} 
rely on developers to supply annotations that describe the locking discipline 
such as which lock protects a specific variable, and detect data races by 
exploiting variable accesses that violate these disciplines. For example, Clang 
thread safety analysis~\cite{ClangThreadSafety} requires developers to label a 
variable and the lock to protect it with a {\tt GUARDED\_BY} attribute. And 
then detects data races by finding variable accesses that violate the given 
attribute. However, such annotation-based approaches are not suitable for race 
detection in OS kernels, because even an expert developer can not provide 
accurate annotations, due to poor documentation and complicated logic of OS 
codes.

@@

Dynamic analysis can acquire run-time information such as memory address, and 
thus complex alias analysis can be avoided. Therefore, some 
approaches~\cite{Lochmann:EuroSys19, Lu:SOSP07, Lu:FSE18, Joshi:ASE08, 
Liu:NSDI07} detect data races dynamically to improve precision. They mine 
implicit code rules in softwares by statistically analyzing execution traces, 
and then use the mined rules to detect related bugs. For example, 
LockDoc~\cite{Lochmann:EuroSys19} records accesses to variables and lock 
acquisitions of an instrumented Linux kernel, and then infers locking rules 
from the recorded accesses. After that, LockDoc automatically locates variables 
access that violate the inferred locking rules to detect concurrency bugs such 
as data races. However, dynamic analysis suffers from low code coverage, and 
thus the locking rules inferred through execution traces can be imprecise. 
Besides, dynamic analyses are hard to deploy, because they need to run OS 
kernels with instruments. At last, it is difficult for dynamic tools to 
estimate the harmfulness of a data race, because race conditions are hard to 
trigger by running the checked software~\cite{Fonseca:DSN10, 
Burckhardt:ASPLOS10, Liu:FSE14, Zhou:EASE15}.

@@

(T1) \sys uses an {\em alias-aware rule mining method} to automatically 
deduce locking rules. We observe that an access to a variable is often 
protected by the lock in the same data structure as the accessed field. And 
this relationship between accessed field and the protecting lock can be 
effectively inferred from a special data structure named alias 
graph~\cite{Li:ASPLOS22, Kastrinis:CC18}. Specifically, fields in the same data 
structure have the same ancestor in the alias graph, and thus whether an 
accessed field and a specific lock are in the same data structure can be 
inferred by finding a common ancestor in the alias graph. Moreover, with 
benefits from precise field-sensitive alias relationships of alias graph, 
\sys can effectively extract the accessed field and its corresponding 
protecting lock. After obtaining the accessed field and protecting lock pairs, 
\sys calculates the proportion of field accesses protected by a specific 
lock in all field accesses. If the proportion is larger than a given threshold, 
the accessed field is determined to be protected by the protecting lock.

(T2) \sys uses a {\em lock-usage analysis} to filter out false positives 
validating concurrency of code paths. After mining locking rules, \sys detects 
data races by checking whether a given variable access violates the 
locking rules. To reduce false negatives, \sys conservatively assumes 
every two functions can be executed concurrently, and thus can introduce false 
positives. However, we observe that each kernel module has an initialization 
phase, after which many functions can be called concurrently by other modules. 
When performing initialization, the kernel module serially initialized the lock 
and prepare other data for subsequent operations. And thus functions with the 
lock initialization and functions called by them tend not to be executed 
concurrently. Based on this observation, \sys extracts all functions 
reachable from the function with a lock initialization operation such as {\tt 
spin\_lock\_init()}, and suppose that this function can not be executed in 
parallel.

### 2023-07-23 2.motivation.tex
Update technique
update

% !TeX spellcheck = en_US
\section{Motivation}
\label{sec_motivation}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=1\linewidth]{figures/fig_bug_demo.pdf}
	\figcaption{A null-pointer dereference due to data race in Linux 6.2.}
	\label{fig_bug_demo}
\end{figure}
Figure~\ref{fig_bug_demo} shows a real null-pointer dereference caused by a 
data race in the Linux DRM driver. In the DRM driver, the functions {\tt 
exynos\_drm\_crtc\_atomic\_disable()} and {\tt exynos\_crtc\_handle\_event()} 
can execute concurrently. We exploit \textcircled{\footnotesize{n}} to 
represent the execution order of instructions and show one execution case in 
the left of Figure~\ref{fig_bug_demo}. In Thread 1, the data structure fields 
{\tt crtc->state->event} and {\tt crtc->state->active} is checked by an if 
statement in the function {\tt exynos\_drm\_crtc\_atomic\_disable()}. After the 
condition is calculated to be true, the function {\tt 
exynos\_crtc\_handle\_event()} is executed in Thread 2. In this function, the 
value of {\tt crtc->state->active} is assigned to {\tt event} 
(\textcircled{\footnotesize{2}}) and then {\tt event} is checked in an if 
statement (\textcircled{\footnotesize{3}}). If it is not NULL, the data 
structure field {\tt crtc->state->event} is assigned with NULL 
(\textcircled{\footnotesize{4}}). Right after this assignment, the function 
{\tt drm\_crtc\_send\_vblank\_event} is called  in Thread 1 
(\textcircled{\footnotesize{6}}) with the argument {\tt crtc->state->active}, 
after acquiring the lock {\tt crtc->dev->event\_lock} 
(\textcircled{\footnotesize{5}}). In the called function, the data structure 
field {\tt crtc->state->event} is dereferenced through {\tt e->pipe} 
(\textcircled{\footnotesize{6}}). In this execution case, the data structure 
{\tt crtc->state->event} is first assigned with NULL and then dereferenced, and 
thus a null-pointer dereference can occur.

@@

\PP{C1: Getting locking rules.} The relationship between variables and locks 
are not well documented in OS kernels, making it hard to determine whether a 
specific data structure field should be protected by a lock and which lock is 
required (locking rules), even for an expert developer. And thus existing 
annotation-based approaches~\cite{Boyapati:OOPSLA02, Anderson:PLDI08, 
Anderson:PLDI09, Zhou:MICRO19, Flanagan:PASTE01, Flanagan:PLDI00, 
Sadowski:PLATEAU14, ClangThreadSafety, Blackshear:OOPSLA18} are difficult to 
apply to race detection in OS kernels. Other approaches~\cite{Choi:PLDI02, 
Engler:SOSP03, Voung:FSE07, Pratikakis:PLDI06, Naik:PLDI06} employ 
lockset-based analysis to detect data races automatically, but they do not 
consider alias relations~\cite{Voung:FSE07, Engler:SOSP03} or just use 
imprecise flow-insensitive alias analysis~\cite{Choi:PLDI02, 	
Pratikakis:PLDI06, Naik:PLDI06}. However, due to the heavy use of pointers and 
data structure fields in OS code, the alias relationships between variables can 
be very complex, and thus lacking effective alias analysis can introduce many 
false locking rules.

>>>>

% !TeX spellcheck = en_US
\section{Background and Motivation}
\label{sec_motivation}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=1\linewidth]{figures/fig_bug_demo.pdf}
	\figcaption{A null-pointer dereference due to data race in Linux 6.2.}
	\label{fig_bug_demo}
\end{figure}
Figure~\ref{fig_bug_demo} shows a real null-pointer dereference caused by a 
data race in the Linux DRM driver. In the DRM driver, the functions {\tt 
exynos\_drm\_crtc\_atomic\_disable()} and {\tt exynos\_crtc\_handle\_event()} 
can execute concurrently. We exploit \textcircled{\footnotesize{n}} to 
represent the execution order of instructions and show one execution case in 
the left of Figure~\ref{fig_bug_demo}. In Thread 1, the variables {\tt 
crtc->state->event} and {\tt crtc->state->active} is checked by an if statement 
in the function {\tt exynos\_drm\_crtc\_atomic\_disable()}. After the condition 
is calculated to be true, the function {\tt exynos\_crtc\_handle\_event()} is 
executed in Thread 2. In this function, the value of {\tt crtc->state->active} 
is assigned to {\tt event} (\textcircled{\footnotesize{2}}) and then {\tt 
event} is checked in an if statement (\textcircled{\footnotesize{3}}). If it is 
not NULL, the variable {\tt crtc->state->event} is assigned with NULL 
(\textcircled{\footnotesize{4}}). Right after this assignment, the function 
{\tt drm\_crtc\_send\_vblank\_event} is called  in Thread 1 
(\textcircled{\footnotesize{6}}) with the argument {\tt crtc->state->active}, 
after acquiring the lock {\tt crtc->dev->event\_lock} 
(\textcircled{\footnotesize{5}}). In the called function, the variable {\tt 
crtc->state->event} is dereferenced through {\tt e->pipe} 
(\textcircled{\footnotesize{6}}). In this execution case, the data structure 
{\tt crtc->state->event} is first assigned with NULL and then dereferenced, and 
thus a null-pointer dereference can occur.

@@

\PP{C1: Getting locking rules.} The relationship between variables and locks 
are not well documented in OS kernels, making it hard to determine whether a 
specific variable should be protected by a lock and which lock is 
required (locking rules), even for an expert developer. And thus existing 
annotation-based approaches~\cite{Boyapati:OOPSLA02, Anderson:PLDI08, 
Anderson:PLDI09, Zhou:MICRO19, Flanagan:PASTE01, Flanagan:PLDI00, 
Sadowski:PLATEAU14, ClangThreadSafety, Blackshear:OOPSLA18} are difficult to 
apply to race detection in OS kernels. Other approaches~\cite{Choi:PLDI02, 
Engler:SOSP03, Voung:FSE07, Pratikakis:PLDI06, Naik:PLDI06} employ 
lockset-based analysis to detect data races automatically, but they do not 
consider alias relations~\cite{Voung:FSE07, Engler:SOSP03} or just use 
imprecise flow-insensitive alias analysis~\cite{Choi:PLDI02, 	
Pratikakis:PLDI06, Naik:PLDI06}. However, due to the heavy use of pointers and 
data structure fields in OS code, the alias relationships between variables can 
be very complex, and thus lacking effective alias analysis can introduce many 
false locking rules.

### 2023-07-23 3.technique.tex
update

\subsection{Alias-Aware Rule Mining Method}
\label{subsec_rule_mining}
The relationship between variables and locks are not well documented in OS 
kernels, but it can be inferred from the kernel code. Specifically, a data 
structure field is often protected by the lock stored in the same data 
structure. And thus if a data structure field is accessed after acquiring a 
lock existing in the same data structure in most cases, the variable is likely 
to be protected by the lock. Whether a data structure field and the protecting 
lock exist in the same data structure can be determined though an alias 
graph~\cite{Li:ASPLOS22, Kastrinis:CC18} by finding their common ancestor. 
Based on this insight, we propose an {\em alias-aware rule mining method} to 
deduce locking rules automatically. Moreover, with benefits from precise 
field-sensitive alias relationships of alias graph, our alias-aware rule mining 
method can find data structure filed and its protecting lock effectively.

\PP{Alias Graph.} It is an important data structure to infer relationships 
between data structure field and its protecting lock in our analysis, so we 
introduce it and its update first.

An alias graph is a 2-tuple $\mathit{G = \left<N, E\right>}$, where 
$\mathit{N}$ is a set of nodes, and each node $\mathit{n}$ represents an alias 
set that points to one abstract object. $\mathit{E}$ is a set of labeled edges. 
Each edge is labeled with a data structure field or a dereference operator 
``$\mathit{*}$'', which represents how an abstract object is accessed.

@@

\noindent{\textbf{\em Example.}} Figure~\ref{fig_alias_graph_demo} shows a 
piece of driver-like source code and its alias graph. In this example, after an 
GEP (\&dev->lock) operation at Line 6, an edge labeled with {\tt lock} from 
node $\mathit{n_1}$ to node $\mathit{n_4}$ is inserted. Similarly, an edge 
labeled with {\tt flag} from node $\mathit{n_1}$ to node $\mathit{n_2}$ is 
inserted after Line 7. At last, an edge labeled with a dereference operator 
($\mathit{*}$) is inserted after the STORE (*fp = f) operation at Line 8. In 
this example, {\tt \&dev->flag} is represented by node $\mathit{n_2}$, and {\tt 
\&dev->lock} is represented by node $\mathit{n_4}$. The two nodes have a common 
ancestor $\mathit{n_1}$, and thus the accessed data structure field {\tt 
\&dev->flag} and the protecting lock {\tt \&dev->lock} can be inferred to exist 
in the same data structure (namely {\tt Dev}).

>>>>

\subsection{Alias-Aware Rule Mining Method}
\label{subsec_rule_mining}
The relationship between variables and locks are not well documented in OS 
kernels, but it can be inferred from the kernel code. Specifically, a variable 
is often protected by the lock stored in the same data structure. And thus if a 
variable is accessed after acquiring a lock existing in the same data structure 
in most cases, it is likely to be protected by the lock. Whether a variable and 
the protecting lock exist in the same data structure can be determined though 
an alias graph~\cite{Li:ASPLOS22, Kastrinis:CC18} by finding their common 
ancestor. Based on this insight, we propose an {\em alias-aware rule mining 
method} to deduce locking rules automatically. Moreover, with benefits from 
precise field-sensitive alias relationships of alias graph, our alias-aware 
rule mining method can find data structure filed and its protecting lock 
effectively.

\PP{Alias Graph.} It is an important data structure to infer relationships 
between variable and its protecting lock in our analysis, so we introduce it 
and its update first.

An alias graph is a 2-tuple $\mathit{G = \left<N, E\right>}$, where 
$\mathit{N}$ is a set of nodes, and each node $\mathit{n}$ represents an alias 
set that points to one abstract object. $\mathit{E}$ is a set of labeled edges. 
Each edge is labeled with a data structure field or a dereference operator 
``$\mathit{*}$'', which represents how an abstract object is accessed. In an 
alias node, a variable residing in a node followed by a sequence of edge
labels form an access path~\cite{Kastrinis:CC18, Cheng:PLDI00}. In this paper, 
we replace the variable in an access path with its structure name to represent 
a data structure field.

@@

\noindent{\textbf{\em Example.}} Figure~\ref{fig_alias_graph_demo} shows a 
piece of driver-like source code and its alias graph. In this example, after an 
GEP (\&dev->lock) operation at Line 6, an edge labeled with {\tt lock} from 
node $\mathit{n_1}$ to node $\mathit{n_4}$ is inserted. Similarly, an edge 
labeled with {\tt flag} from node $\mathit{n_1}$ to node $\mathit{n_2}$ is 
inserted after Line 7. At last, an edge labeled with a dereference operator 
($\mathit{*}$) is inserted after the STORE (*fp = f) operation at Line 8. The 
final alias graph is shown in Figure~\ref{fig_alias_graph_demo}(b), and access 
paths are shown in the bottom left corner. Take node $\mathit{n_3}$ as an 
example, it can represent two fields, one is {\tt Dev.flag*}, and the other is 
{\tt int\_pointer*} (we exploit int\_pointer to represent a pointer points to 
an integer, and regard it as a data structure for convenience).

\begin{figure}[htbp]
	\centering
	\includegraphics[width=1\linewidth]{figures/fig_pseudocode_get_access.pdf}
	\figcaption{Pseudocodes to get accessed field and protecting lock.}
	\label{fig_pseudocode_get_access}
\end{figure}

Given an alias graph, whether a variable and a lock exist in the same data 
structure can be determined by finding a common ancestor. If they are in the 
same data structure, the lock is likely to protect the variable when it is 
accessed. Figure~\ref{fig_pseudocode_get_access} shows the pseudocode to 
get the field of the accessed variable and the field of the protecting lock in 
the form of access path, if they exist in the same data structure. Given a node 
of an accessed variable and a node of a lock variable, the analysis first gets 
the common ancestor of the two nodes (Line 1). And then, if the common ancestor 
does not exist, the analysis returns NULL (Lines 2-3). Otherwise, the analysis 
gets the access path for the node of the accessed variable and the node of the 
lock variable from the common ancestor (Lines 5-7).

%\begin{table}[htbp]
%	\tablecaption{Notation table of pseudocodes.}
%	\label{tbl_notation}
%	\centering
%	\scriptsize
%	\begin{spacing}{0.98}
%		\begin{tabular}{@{ }p{2.7cm}p{5.05cm}@{ }}
%		\toprule[1pt]
%		GetAliasNode($\mathit{var}$, $\mathit{alias\_graph}$) & Get the node 
%		the variable $\mathit{var}$ exists in from the alias graph 
%		$\mathit{alias\_graph}$. \\ \hline
%		GetCommonAncestor($\mathit{node_1}$, $\mathit{node_2}$) & Get the 
%		common ancestor of the two nodes $\mathit{node_1}$ and 
%		$\mathit{node_2}$. \\ \hline
%		GetAccessPath($\mathit{node_1}$, $\mathit{node_2}$) & Get the access 
%		path from $\mathit{node_1}$ to $\mathit{node_2}$ \\ \hline
%		\bottomrule[1pt]	
%		\end{tabular}
%	\end{spacing}
%\end{table}

Take the alias graph in Figure~\ref{fig_alias_graph_demo} as an example, {\tt 
\&dev->flag} is represented by node $\mathit{n_2}$, and {\tt \&dev->lock} is 
represented by node $\mathit{n_4}$. The two nodes have a common ancestor 
$\mathit{n_1}$, and thus the accessed variable {\tt \&dev->flag} and the 
protecting lock {\tt \&dev->lock} can be inferred to exist in the same data 
structure (namely {\tt Dev}). Therefore, the structure field Dev.flag is likely 
to be protected the lock stored in the structure field Dev.lock.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=1\linewidth]{figures/fig_workflow.pdf}
	\figcaption{Workflow of locking-rule mining.}
	\label{fig_workflow}
\end{figure}

Based on the alias graph, our alias-aware rule mining method performs an 
inter-procedural path-based~\cite{Li:ASPLOS22}, field-sensitive and alias-aware 
analysis to effectively mine locking rules about whether a specific variable 
should be protected by a lock and which lock is required. Overall, our 
alias-aware rule mining method has three main stages shown in 
Figure~\ref{fig_workflow}. In Stage 1, it extract key variable that may be 
protected by a lock. In Stage 2, it collect all accesses to key fields as well 
as code paths these accesses exist in. In Stage 3, it deduce locking rules by 
calculate the proportion of field accesses protected by a specific lock in all 
field accesses.

\PP{S1: Key-field Extraction.} The OS Kernel has a large code base with 
numerous variables. However, only a small part of variables should be protected 
by a specific lock, and thus collecting all variable accesses can introduce 
much unnecessary overhead. Generally, only a few field accesses can miss 
necessary protecting lock, due to carelessness of developers. Based on this 
insight, our analysis first extracts key fields that may need to be protected 
by a specific lock, by performing a lock-set analysis to find whether a given 
variable is accessed after acquiring a lock in the same data structure as the 
accessed field in any code path.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{figures/fig_pseudocode_lock_set.pdf}
	\figcaption{Pseudocodes of lock-set analysis.}
	\label{fig_pseudocode_lock_set}
\end{figure}

Figure~\ref{fig_pseudocode_lock_set} shows the lock-set analysis based on alias 
graph. The analysis first gets the operand of the instruction (Line 1), and 
then get the node of the operand from the alias graph (Line 2). If the 
instruction is a lock operation, the node of the operand is inserted into the 
lock set (Lines 3-4). Otherwise, if the instruction is an unlock operation, the 
node of the operand is removed from the lock set (Lines 5-6).

\begin{figure}[htbp]
	\centering
	\includegraphics[width=1\linewidth]{figures/fig_pseudocode_field_extract.pdf}
	\figcaption{Pseudocodes of key-field extraction.}
	\label{fig_pseudocode_field_extract}
\end{figure}

Figure~\ref{fig_pseudocode_field_extract} shows the pseudocode to collect key 
fields that may be protected by a specific lock when are accessed, based on 
lock-set analysis and alias graph. The analysis start analyzing

For each function without a caller function, the analysis

### 2023-07-23 paper.tex
Add motivation
Update technique
update

\usepackage[normalem]{ulem}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{xspace}

@@

@@

@@

To take advantage of multiple-core architecture of modern CPUs, an operating 
system (OS) is expected to handle concurrency, inevitably introducing many 
concurrent issues. And data race is one of the most harmful concurrent issues 
that can trigger memory or logical bugs. A data race is caused by wrongly 
accessing shared data in different threads. To ensure correct access to shared 
data, fine-grained locking mechanisms are introduced. However, it is hard to 
determine whether a lock should be used for a specific data structure field 
(locking rules) even for an expert developer, due to poor documentation and 
complicated logic of OS code. As a result, OS kernel is prone to data races, 
because necessary locks may be missed by mistake. Static analysis is a common 
technique to help improve code quality, but it is quite challenging to detect 
data races in OS kernels automatically, because of lack of knowledge of locking 
rules and high complexity of concurrent execution.

>>>>

\usepackage[normalem]{ulem}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{xspace}
\usepackage{xstring}

@@

\newtheorem{definition}{Definition}
\newtheorem{example}{Example}

@@

\newcommand{\figcaption}{% 
	\setlength{\abovecaptionskip}{4pt}%	\setlength{\belowcaptionskip}{1pt}% 
	\caption}

\newcommand{\tablecaption}{% 
	\setlength{\abovecaptionskip}{6pt}%
	\setlength{\belowcaptionskip}{2pt}% 
	\caption}

\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}

\newcommand{\PP}[1]{
	\vspace{2px}
	\noindent{\bf \IfEndWith{#1}{.}{#1}{#1.}}
}

@@

To take advantage of multiple-core architecture of modern CPUs, an operating 
system (OS) is expected to handle concurrency, inevitably introducing many 
concurrent issues. And data race is one of the most harmful concurrent issues 
that can trigger memory or logical bugs. A data race is caused by wrongly 
accessing shared data in different threads. To ensure correct access to shared 
data, fine-grained locking mechanisms are introduced. However, it is hard to 
determine whether a lock should be used for a specific variable (locking rules) 
even for an expert developer, due to poor documentation and complicated logic 
of OS code. As a result, OS kernel is prone to data races, because necessary 
locks may be missed by mistake. Static analysis is a common technique to help 
improve code quality, but it is quite challenging to detect data races in OS 
kernels automatically, because of lack of knowledge of locking rules and high 
complexity of concurrent execution.
